% !TEX root = ../thesis.tex
As our collision is defined in the space of normalized cumulants but our analysis uses moments, we have to link their corresponding expansions.
We start by expanding the first nontrivial normalized cumulant $K_{11}$, defined in~\eqref{eq: K 11 from moments}, the same way we expanded the moments in~\eqref{eq: expansion of m} and explain a few concepts, before diving into all the expansions.
We can reformulate~\eqref{eq: K 11 from moments} like
\begin{equation}
  \label{eq: first expansion}
  \begin{aligned}
    K_{11} & = m_{11} - \frac{m_{10}m_{01}}{m_{00}}\\
    \Leftrightarrow
    \sum_{i=0}^\infty \epsilon^i K_{11}^{(i)}
    & = \sum_{i=0}^\infty \epsilon^i m_{11}^{(i)} -
    \frac{\sum_{i,j=0}^\infty \epsilon^{i+j} m_{10}^{(i)}m_{01}^{(j)}}
        {\sum_{i=0}^\infty \epsilon^i m_{00}^{(i)}}.
  \end{aligned}
\end{equation}
We have to stop here and cope with the denominator first.
In writing
\begin{equation}
  \frac{1}{\sum_{i=0}^\infty \epsilon^i m_{00}^{(i)}}=
  \frac{1}{m_{00}^{(0)}}
  \frac{1}{1 - \sum_{i=1}^\infty \epsilon^i \frac{ - m_{00}^{(i)}}{ m_{00}^{(0)}}}.
\end{equation}

we prepared the denominator to be coped with a geometric series.
This is valid as long as we assume $\epsilon$ to be `small enough' to ensure $\abs{\sum_{i=1}^\infty \epsilon^i \frac{ m_{00}^{(i)}}{ m_{00}^{(0)}} } < 1$.
This is by no means a bold statement, as firstly the zeroth order of $m_{00}$ is left out and all other terms are divided by the constant portion of $m_{00}$.
Secondly, our nondimensionalisation in~\eqref{eq: nondimensionalisation} states that $\epsilon = \frac{\Delta x}{L}$, where $L$ is a typical length in our project.
As our typical length scales have to be some orders of magnitude larger than our cell spacing\footnote{Let's say we discretize a 2D wing with a given chord length, we have to take small cells in its vicinity just to represent the shape accurately.}, our prerequesite is even less of a problem.

Thus, we get
\begin{equation}
  \label{eq: definition of g}
  g(\epsilon) \defined \sum_{j=0}^\infty {\left(\sum_{i=1}^\infty \epsilon^i \frac{ - m_{00}^{(i)}}{ m_{00}^{(0)}}\right)}^j = \frac{1}{1 - \sum_{i=1}^\infty \epsilon^i \frac{ - m_{00}^{(i)}}{ m_{00}^{(0)}}}.
\end{equation}
Expanding this term and using the even and odd order properties of equation~\eqref{eq: kill even moments odd order} and following, we get
\begin{equation}
  \label{eq: expand g}
  \begin{aligned}
    g(\epsilon) = & \underbrace{1}_{j=0} - \epsilon \underbrace{ \frac{m_{00}^{(1)}}{m_{00}^{(0)}}}_{j=1,i=1}
    + \epsilon^2 \Bigg(
      \underbrace{\frac{m_{00}^{{(1)}^2}}{m_{00}^{{(0)}^2}}}_{j=2,i=1}
      - \underbrace{\frac{m_{00}^{(2)}}{m_{00}^{(0)}}}_{j=1,i=2} \Bigg) + O(\epsilon^3)
      \\=&
      1 - \epsilon^2 \frac{m_{00}^{(2)}}{m_{00}^{(0)}}  + O(\epsilon^3)
  \end{aligned}
\end{equation}
% 1 - \epsilon^2 \frac{m_{00}^{(2)}}{m_{00}^{(0)}}  + O(\epsilon^3)

Now we finally analyze the cumulant $K_{11}$.
Restarting at equation~\eqref{eq: first expansion} and inserting equations~\eqref{eq: definition of g} and~\eqref{eq: expand g}, we get

\begin{equation}
  \begin{aligned}
    \sum_{i=0}^\infty \epsilon^i K_{11}^{(i)}
    & = \sum_{i=0}^\infty \epsilon^i m_{11}^{(i)} -
    \frac{\sum_{i,j=0}^\infty \epsilon^{i+j} m_{10}^{(i)}m_{01}^{(j)}}
        {\sum_{i=0}^\infty \epsilon^i m_{00}^{(i)}} \\
    \Leftrightarrow
    \sum_{i=0}^\infty \epsilon^i K_{11}^{(i)}
    & = \sum_{i=0}^\infty \epsilon^i m_{11}^{(i)} -
    \frac{\sum_{i,j=0}^\infty \epsilon^{i+j} m_{10}^{(i)}m_{01}^{(j)}}
    {m_{00}^{(0)}}
    g(\epsilon)\\
    \Leftrightarrow
  \sum_{i=0}^\infty \epsilon^i K_{11}^{(i)}
   & = \sum_{i=0}^\infty \epsilon^i m_{11}^{(i)} -
  \frac{\sum_{i,j=0}^\infty \epsilon^{i+j} m_{10}^{(i)}m_{01}^{(j)}}
      {m_{00}^{(0)}}
  \left(1 - \epsilon^2 \frac{m_{00}^{(2)}}{m_{00}^{(0)}}  + O(\epsilon^3)\right).
\end{aligned}
\end{equation}
Collecting all zeroth order terms, we get using~\eqref{eq: zeroth order velocity zero}
\begin{equation}
  K_{11}^{(0)} = m_{11}^{(0)} - \frac{m_{01}^{(0)}m_{10}^{(0)}}{m_{00}^{(0)}} =  m_{11}^{(0)}.
\end{equation}
Analogously, for first order terms,
\begin{equation}
  \begin{aligned}
    K_{11}^{(1)} & = m_{11}^{(1)} - \frac{m_{01}^{(1)}m_{10}^{(0)}+m_{01}^{(0)}m_{10}^{(1)}}{m_{00}^{(0)}}
    \\
    &= m_{11}^{(1)} = 0
  \end{aligned}
\end{equation}
holds.
Thus, the normalized cumulant $K_{11}$ is equal to the corresponding moment at order zero and one.

Going on to the second order terms, we find
\begin{equation}
  \begin{aligned}
    K_{11}^{(2)}
    = &m_{11}^{(2)}
    - \frac{
      m_{10}^{(1)}m_{01}^{(1)}
    + m_{10}^{(0)}m_{01}^{(2)}
    + m_{10}^{(2)}m_{01}^{(0)}
    }{m_{00}^{(0)}}
    + \frac{m_{10}^{(0)}m_{01}^{(0)}}{m_{00}^{(0)}}
    \frac{m_{00}^{(2)}}{{m_{00}^{(0)}}}
    \\ = &
    m_{11}^{(2)}
    - \frac{ m_{10}^{(1)}m_{01}^{(1)}}{m_{00}^{(0)}},
  \end{aligned}
\end{equation}
which depicts a first discrepancy of the corresponding moment.

Due to the fact that the remaining calculations are just tedious but not really difficult, they are relegated to Appendix~\ref{appendix: Expansions of the normalized cumulants}.
The complete list of expansions is in equations~\eqref{eq: expansions of cumulants zeroth order raw} through~\eqref{eq: expansions of cumulants second order raw}.

Anticipating the findings of the next
section\footnote{Those only use equations~\eqref{eq: expansions of cumulants zeroth order raw} through~\eqref{eq: expansions of cumulants second order raw}, so this is fine.}, the simplified equations are presented here.
The zeroth order expansions can be simplified using equations~\eqref{eq: eq moments 11_0},~\eqref{eq: eq moments 20_0},~\eqref{eq: eq moments 02_0} and~\eqref{eq: eq moments 22_0} together with equations~\eqref{eq: zeroth order invariant} and~\eqref{eq: first order invariant} to give
\begin{equation}
  \label{eq: expansions of cumulants zeroth order}
  \begin{aligned}
    K_{10}^{(0)} =&\ m_{10}^{(0)} = 0\\
    K_{01}^{(0)} =&\ m_{01}^{(0)} = 0\\
    K_{11}^{(0)} =&\ m_{11}^{(0)} = 0\\
    K_{20}^{(0)} =&\ m_{20}^{(0)} = c_s^2 m_{00}^{(0)}\\
    K_{02}^{(0)} =&\ m_{02}^{(0)} = c_s^2 m_{00}^{(0)}\\
    K_{21}^{(0)} =&\ m_{21}^{(0)} = 0\\
    K_{12}^{(0)} =&\ m_{12}^{(0)} = 0\\
    K_{22}^{(0)} =&\ m_{22}^{(0)} - \frac{ m_{20}^{(0)} m_{02}^{(0)} }{m_{00}^{(0)}} - 2\frac{ m_{11}^{{(0)}^2}}{m_{00}^{(0)}} = 0
  \end{aligned}
\end{equation}
The first order terms will use again~\eqref{eq: eq moments 11_0},~\eqref{eq: eq moments 20_0} and~\eqref{eq: eq moments 02_0} together with~\eqref{eq: eq moments 21_1} and~\eqref{eq: eq moments 12_1}
\begin{equation}
  \label{eq: expansions of cumulants first order}
  \begin{aligned}
    K_{10}^{(1)} =&\ m_{10}^{(1)}\\
    K_{01}^{(1)} =&\ m_{01}^{(1)}\\
    K_{11}^{(1)} =&\ m_{11}^{(1)} = 0 \\
    K_{20}^{(1)} =&\ m_{20}^{(1)} = 0\\
    K_{02}^{(1)} =&\ m_{02}^{(1)} = 0\\
    K_{21}^{(1)} =&\ m_{21}^{(1)}
    - c_s^2 m_{01}^{(1)} = 0 \\
    K_{12}^{(1)} =&\ m_{21}^{(1)}
    - c_s^2 m_{10}^{(1)} = 0 \\
    K_{22}^{(1)} =&\ m_{22}^{(1)} = 0
  \end{aligned}
\end{equation}
Whats remaining is the expansion of the second order terms.
Here, only the expansion of $K_{22}$ can be simplified, using the same equations like in the derivation of~\eqref{eq: expansions of cumulants first order}.
Be aware, that the second order terms in equation~\eqref{eq: eq moments 11_2} and following cannot be replaced by the nonequilibrium terms.
\begin{equation}
  \label{eq: expansions of cumulants second order}
  \begin{aligned}
    K_{10}^{(2)} =&\ m_{10}^{(2)} = 0\\
    K_{01}^{(2)} =&\ m_{01}^{(2)} = 0\\
    K_{11}^{(2)} =&\ m_{11}^{(2)} - \frac{ m_{10}^{(1)}m_{01}^{(1)}}{m_{00}^{(0)}} \\
    K_{20}^{(2)} =&\ m_{20}^{(2)} - \frac{ m_{10}^{{(1)}^2}}{m_{00}^{(0)}} \\
    K_{02}^{(2)} =&\ m_{02}^{(2)} - \frac{ m_{01}^{{(1)}^2}}{m_{00}^{(0)}} \\
    K_{12}^{(2)} =&\ m_{12}^{(2)} = 0\\
    K_{21}^{(2)} =&\ m_{21}^{(2)} = 0\\
    K_{22}^{(2)}
    = &\
    m_{22}^{(2)}
    \\&
    - 2 c_s^2 \frac{ m_{10}^{{(1)}^2} }{m_{00}^{(0)}}
    - 2 c_s^2 \frac{ m_{01}^{{(1)}^2} }{m_{00}^{(0)}}
    \\&
    - c_s^2 m_{02}^{(2)}
    - c_s^2 m_{20}^{(2)}
    + c_s^4 m_{00}^{(2)}
    \\&
    + 2 c_s^2\frac{ m_{10}^{{(1)}^2} }{m_{00}^{(0)}}
    + 2 c_s^2\frac{ m_{01}^{{(1)}^2} }{m_{00}^{(0)}}
    \\= &\
    m_{22}^{(2)}
    + c_s^2\left(c_s^2 m_{00}^{(2)}
    - m_{02}^{(2)}
    - m_{20}^{(2)}
    \right)
  \end{aligned}
\end{equation}
